\vspace{-10mm}\bf \mytitle

### 2021-11-24 ms.Rnw
adding reference to published article

@@

\spacingset{1.45} % DON'T change the spacing!

@@

slice_abf_mcap <- panelPomp::mcap(
  lp=slice_abf_results[,"logLik"],
  parameter=slice_abf_results[,"g"],
  lambda = 1
)

slice_ubf_mcap <- panelPomp::mcap(
  lp=slice_ubf_results[,"logLik"],
  parameter=slice_ubf_results[,"g"],
  lambda = 0.8
)

slice_bpf_mcap <- panelPomp::mcap(
  lp=slice_bpf_results[,"logLik"],
  parameter=slice_bpf_results[,"g"],
  lambda = 1
)

slice_enkf_mcap <- panelPomp::mcap(
  lp=slice_enkf_results[,"logLik"],
  parameter=slice_enkf_results[,"g"],
  lambda = 1
)

>>>>

\vspace{3mm}

\noindent This document is a reproducible version of \citet{ionides21} compiled on \today, using R version \Sexpr{getRversion()}, \code{pomp} version \Sexpr{packageVersion("pomp")} and \code{spatPomp} version \Sexpr{packageVersion("spatPomp")}.

@@

%\spacingset{1.45} % DON'T change the spacing!
\spacingset{1}

@@

slice_abf_mcap <- mcap(
  lp=slice_abf_results[,"logLik"],
  parameter=slice_abf_results[,"g"],
  lambda = 1
)

slice_ubf_mcap <- mcap(
  lp=slice_ubf_results[,"logLik"],
  parameter=slice_ubf_results[,"g"],
  lambda = 0.8
)

slice_bpf_mcap <- mcap(
  lp=slice_bpf_results[,"logLik"],
  parameter=slice_bpf_results[,"g"],
  lambda = 1
)

slice_enkf_mcap <- mcap(
  lp=slice_enkf_results[,"logLik"],
  parameter=slice_enkf_results[,"g"],
  lambda = 1
)
